---
title: "Lab_7_ilay"
author: "Ilayda Dinc"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey!,mn,mn
Hey yourself!n

I am the collaborater
load tidyverse
read in kermit
side histograms scare.pre fort all respondent seperated by gender

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist
```
Creator: Perform rank-based comparisons using Mann Whitney U t and wilcoxon signed rank
Question: Is there a significant difference in pre-talk ranks of Kermit for Male and female respondents?

```{r}
mwu_kermit <-kermit %>%
  wilcox.test(Score.pre ~ Gender,data= .)

# null : ther e is not a significant difference in ranks for male and female respondents

# alternative : there IS a significant difference in ranks

mwu_kermit

#retain null
```

there was no significant difference in ranks for male and female respondents (W= 155.5, p= 0.4, alpha = 0.05)